Dynamics Analysis: The Sound of Teaching Music 1

### 2022-06-26 experiment-1/analysis/stats/dynamics.Rmd
add some additional analysis for nomalised KV diff
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

@@

>>>>

- Additional analysis based on reviewers' comments

@@

# Additional analysis
- Normalise KV difference by the range of KV value between forte and piano for each participant.

```{r, echo = FALSE}
# normalise diff by KV range
vel_diff_dyn$NormalisedDiff <- 0
for (i in unique(vel_diff_dyn$SubNr)){
  vel_diff_dyn[SubNr == i & Condition == "teaching"]$NormalisedDiff <- vel_diff_dyn[SubNr == i & Condition == "teaching"]$Mean/(max(vel_dyn[SubNr == i & Condition == "teaching"]$Mean)-min(vel_dyn[SubNr == i & Condition == "teaching"]$Mean))
  vel_diff_dyn[SubNr == i & Condition == "performing"]$NormalisedDiff <- vel_diff_dyn[SubNr == i & Condition == "performing"]$Mean/(max(vel_dyn[SubNr == i & Condition == "performing"]$Mean)-min(vel_dyn[SubNr == i & Condition == "performing"]$Mean))
}
vel_diff_dyn

# group
vel_diff_dyn_all_2 <- vel_diff_dyn[, .(N = .N, NormalisedMean = mean(NormalisedDiff), SD = sd(NormalisedDiff), SEM = sd(NormalisedDiff)/sqrt(.N)), by = .(Condition, Skill, Subcomponent)]
vel_diff_dyn_all_2
```

## Plot
```{r, echo = FALSE}
vel_diff_dyn_plot_2 <- data.table(subject = vel_diff_dyn[Condition == "teaching"]$SubNr, teaching = vel_diff_dyn[Condition == "teaching"]$NormalisedDiff, performing = vel_diff_dyn[Condition == "performing"]$NormalisedDiff, subcomponent = vel_diff_dyn[Condition == "teaching"]$Subcomponent)

ggpaired(vel_diff_dyn_plot_2, cond = "performing", cond2 = "teaching", color = "condition", facet.by = "subcomponent", line.size = 0.3, line.color = "gray", xlab = "Condition", ylab = "Normalised KV (0-127)", title = "KV-Diff: Dynamics")
```

## Stats
```{r, echo = FALSE}
# stats
vel_diff_dyn_aov_2 <- aov_car(NormalisedDiff ~ Condition*Subcomponent + Error(SubNr/(Condition*Subcomponent)), vel_diff_dyn)
summary(vel_diff_dyn_aov_2)
```
